---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# fillr
<!-- badges: start -->
  [![Travis build status](https://travis-ci.org/jelger12/fillr.svg?branch=master)](https://travis-ci.org/jelger12/fillr)
  [![Codecov test coverage](https://codecov.io/gh/jelger12/fillr/branch/master/graph/badge.svg)](https://codecov.io/gh/jelger12/fillr?branch=master)
  
<!-- badges: end -->
Fillr is an R package. The goal of fillr is to edit vectors to fill missing values, based on the vector itself. These functions are best used on variables within a grouped data frame.

## Installation

You can install fillr from github with:

``` r
devtools::install_github("jelger12/fillr")
```

## Example

When you want to fill values in a vector with another value, the fillr functions can be used to impute all NA values based on some set rules.

```{r example}
## basic example code

## Fill the NA with the minimum, maximum or last value
fillr::fill_missing_min(c(1, 2, 1, 1, NA))
fillr::fill_missing_max(c(1, 2, 1, 1, NA))
fillr::fill_missing_last(c(1, NA, 1, 2, NA))

## Fill the NA with the same value, only when all non-NA values are the same
fillr::fill_missing_strict(c(1, NA, 1, 1, NA))
fillr::fill_missing_strict(c("a", NA, "a", "a", NA))

## Fill the NA with the previous value (repeating with multiple repeating NA)
fillr::fill_missing_previous(c(1, NA, 1, 2, NA, NA))
```
